### 2014-07-11 Paper_v1.tex
New sections

We modified our particle swarm identification strategy to simultaneously search over control structures and kinetic parameters (Fig. ZZZ). 
We constructed five putative network models, each with the same enzymatic connectivity but different allosteric structures (Fig. ZZZ). 
We then initialized a population of particles, each with one of the five putative regulatory programs, and randomized kinetic parameters.
We biased the distribution of the particle population according to \textit{a~prior} belief of the correct regulatory program.
To this end, we considered three different priors, a uniform distribution where each of the regulatory structures represented 20\% of the population, and
two mixed distributions that were positively and negatively biased towards the correct structure (Table ZZ).

>>>>

We modified our particle swarm identification strategy to simultaneously search over control structures and kinetic parameters (Fig. ZZZ). 
We constructed five putative network models, each with the same enzymatic connectivity but different allosteric structures (Fig. ZZZ). 
We then initialized a population of particles, each with one of the five putative regulatory programs, and randomized kinetic parameters.
We biased the distribution of the particle population according to \textit{a~prior} belief of the correct regulatory program.
To this end, we considered three different priors, a uniform distribution where each regulatory structure represented 20\% of the population, and
two mixed distributions that were positively or negatively biased towards the correct structure (Table ZZ).
